\emeszida

### 2024-03-29 sigbovik/paper.tex
fix url

\section*{Acknowledgments}
The search for these tablets and our effort to understand them was inspired by Ramsey Nasser's \textarabic{قلب} programming language (https://github.com/nasser/---).

>>>>

\section*{Acknowledgments}
The search for these tablets and our effort to understand them was inspired by Ramsey Nasser's \textarabic{قلب} programming language (\url{https://github.com/nasser/---}).
